### 2022-11-22 dissertation/chapters/09-conclusion.tex
✨ (conclusion): Done

\begin{quote}
      \textit{
            I am sorry to have made such a long speech, but I did not have time to make a shorter one. - Winston Churchill
      }
\end{quote}

Finally, the research objectives that have been set out in this dissertation must be concluded. This chapter provides a summary of the research that has been done.

The remainder of the chapter is structured as follows:

\begin{itemize}
      \item \textbf{Section \ref{sec:conclusion:research_goals}} provides a review of the problem statement, objectives and motivations behind the research.

@@

      \item \textbf{Section \ref{sec:conclusion:bhh}} provides a brief recap of the \ac{BHH} and its implementation.

      \item \textbf{Section \ref{sec:conclusion:methodology}} provides a brief recap of the methodology and the empirical process that was followed.

      \item \textbf{Section \ref{sec:conclusion:results}} summarises the research findings.

      \item \textbf{Section \ref{sec:conclusion:further_research}} discuss further research opportunities.

      \item \textbf{Section \ref{sec:conclusion:documentation_and_data}} briefly discusses some supplementary and supporting material related to the research, as made available by the authors either as external sources or in the appendices of this dissertation.

      \item Finally, \textbf{Section \ref{sec:conclusion:closing_statements}} provides the closing statements of the dissertation.
\end{itemize}

\section{Reviewing Research Objectives}
\label{sec:conclusion:research_goals}

@@

The main area of focus for this research stems from the problem statement which identified the difficult and tedious problem of heuristic selection for \ac{FFNN} training. Often times this process is non-trivial and very time-consuming. It has been identified that there is no easy way to know which heuristic to select to train \acp{FFNN}. Traditionally, an iterative approach of trial-and-error was followed. This process involves a tedious process of careful consideration and selection, often at the expense of the researcher's resources.  This research has identified the possibility of using a relatively new approach, referred to as \acp{HH} to automate this selection process. \ac{HH} has been shown to provide a general solution to this problem. The consequences of such approach being successful could provide a mechanism that saves a lot of time and could provide a more generalised solution to heuristic selection.

Investigation was done into the landscapes of existing solutions to train \acp{FFNN} as well as \acp{HH}. Though there exists many applications of \acp{HH} there are little to no published work on using \acp{HH} to train \acp{FFNN}. The only work that was found include the work by~\citeauthor{ref:nel:2021}~\cite{ref:nel:2021}.

Other existing techniques from other problem domains were investigated. \ac{RL}, meta-learning, online, one-shot and probabilistic learning approached were considered. Bayesian probability theory showed promise and the \Ac{BHH} was conceptualised.

The research objectives were defined and are summarised as follows:

\begin{itemize}
      \item Conduct literature studies on all related topics that are relevant to the development of the \ac{BHH}. These include \ac{ANN}, \index{heuristic}heuristics/optimisers, meta-learning, \acp{HH}, probability theory and Bayesian statistics.

      \item Develop a novel \ac{BHH} that has both a selective and perturbative element. For the selection mechanism, Bayesian statistics and \ac{MAP} is used. For the perturbative element, proxied low-level \index{heuristic}heuristic update steps are used.

@@

      \item Conduct an empirical study to study the behavioural characteristics of the \ac{BHH}.

      \item Conduct an empirical study to critically evaluate the performance of the \ac{BHH} to those of traditional, low-level \index{heuristic}heuristic when training \acp{FFNN} on a number of different datasets.

      \item Conduct an empirical study to evaluate variants of the \ac{BHH} to study the impacts of various design decisions on the outcomes of the \ac{BHH}.

      \item Provide a statistically sound evaluation of outcomes with statistical significance tests driving the conclusions of the outcomes.
\end{itemize}

As one can see, the research set out to do in this dissertation was quite extensive and also identifies many different opportunities for future research.

The next sections aim to provide brief summaries of the work that was done, followed by a conclusion of the outcomes of each.

@@

Chapters \ref{chap:introduction} - \ref{chap:probability} provided the reader with background information that is necessary to understand the components that are discussed and developed in this work. These chapters respectively provided background information, literature reviews and landscape analyses into \acp{ANN}, \index{heuristic}heuristics/optimisers, \acp{HH} and meta-learning, probability theory and Bayesian statistics.

It should be mentioned that there are many resources available on the above mentioned topics in their own right. However, the intersection of these topics, especially \acp{ANN} and \acp{HH} are close to non-existent and calls for much more research and publication. This dissertation aims to provide a manifesto of these topics and how they are bring together to show that \acp{HH} can be used to train \acp{FFNN}.

From these topics, it can be concluded that the necessary background information that was provisioned for in the objectives for the dissertation have been provided. The next section gives a summary of the novel \ac{BHH} that was developed.

\section{Summary of Bayesian Hyper-Heuristics}
\label{sec:conclusion:bhh}

The main takeaway point from this dissertation is the development of a novel \ac{BHH}. Chapter \ref{chap:bhh} provides the details and implementation of the \ac{BHH} and provides the reader with various design decisions that could control/affect the outcomes of the \ac{BHH}.

It was shown how the \ac{BHH} implements a Bayesian probabilistic model and makes use of online learning to select \index{heuristic}heuristics dynamically throughout the training process. This probabilistic model forms the selection mechanism for the \ac{BHH}.

Furthermore, it is shown that selection alone is not enough and that a measure of transition between \index{heuristic}heuristics is needed. Entity and \index{heuristic}heuristic state and state-manipulation formed the cornerstone of this topic. A technique that deconstructs \index{heuristic}heuristics into their initialisation and update steps is proposed. This technique then allows for the proxying of update step operations as they are required by different \index{heuristic}heuristics. Though this solves the transition problem between \index{heuristic}heuristics, is has been indicated that does not guarantee stable search processes. This does raise opportunities for further research which is summarised below in Section \ref{sec:conclusion:further_research}.

The simplicity of the \ac{BHH} and various challenges related to it have been highlighted. Of these challenge include:

\begin{itemize}
      \item Catering for overfitting by early stopping conditions.
      \item Catering for invalid selections.
      \item Catering for invalid or stale entity and \index{heuristic}heuristic states.
      \item Catering for mode-collapse where a \index{heuristic}heuristic is either always selected or never selected.
      \item Catering for a trade-off between exploration and exploitation.
\end{itemize}

After the development of the \ac{BHH}, the authors presented the methodology used to execute the empirical process. The details of which is summarised in the next section.

@@

As discussed above, the research objectives defined a number of empirical tests to be executed. Each one of the empirical tests is referred to as an experimental group. Various experimental groups have been identified and is listed below:

\begin{itemize}
      \item A case-study on the behaviour of the \ac{BHH} during training and testing to understand the workings of the \ac{BHH} and to see if the \ac{BHH} is able to train \acp{FFNN}.
      \item A comparative analysis between the performance of standalone \index{heuristic}heuristics and the baseline \ac{BHH} when training \acp{FFNN}.
      \item A comparative analysis between variants of the \ac{BHH} that include:
            \begin{itemize}
                  \item Different \index{heuristic}heuristic pool configurations.
                  \item Different population sizes.
                  \item Different credit assignment strategies.
                  \item Different reselection window sizes.
                  \item Different replay window sizes.
                  \item Different reanalysis window sizes.
                  \item Different burn in window sizes.
                  \item Enabling and disabling normalisation of pseudo counts in the performance log.
                  \item Enabling and disabling discounted rewards of pseudo counts in the performance log.
            \end{itemize}
\end{itemize}

Each experimental group is run against a set of 15 datasets, consisting of regression and classification problems, split between uni- and multimodal problems. Each experimental group is repeated over 30 runs for statistical certainty. The statistical analysis process was discussed and ANOVA, post hoc Tukey, independent T-test and Kruskal-Wallis formed part of the statistical test repertoir.

In order to allow for the studying of the \ac{BHH} even after training has saturated and overfitting has occured, all experimental groups are run for 30 epochs, way more than what has been empirically found to be necessary. This also meant that no early stopping conditions were used.

The next section provides a summary of all the results, findings and conclusions related to the empirical process is given next.

@@

All empirical tests where successfully executed and statistically evaluate as described in the methodology presented in Chapter \ref{chap:methodology}. From these evaluations a number of conclusions are made, each described briefly in the sub-sections below:

\subsection{\ac{BHH} behavioural case study}
\label{sec:conclusion:results:summary:case_study}

For this experimental group it was found that the \ac{BHH} is able to train \acp{FFNN} relatively well. It was shown how the \ac{BHH} is able to learn and that the learning is in a positive direction towards the overall objectives of the \ac{BHH}. Furthermore, it was shown in isolation that both the selection mechanism as well as the perturbative component of the \ac{BHH} was successful in their own rights, resulting in a \ac{HH} that is able to select and combine \index{heuristic}heuristics as needed.

It was shown how the \ac{BHH} drastically overfits at some point during training for a number of datasets. Although it is known that early stopping conditions would prohibit this from happening, other solutions have also been proposed. These include:

\begin{itemize}
      \item \index{heuristic}Heuristic selection acceptance criteria: where a selection is only deemed valid if it does indeed improve on performance.

      \item State reset: to avoid overshooting solutions due to momentum.

      \item Various techniques to balance exploration and exploitation.
\end{itemize}

Various example plots on training and test datasets have been provided and detailed plots of the inner-workings of the \ac{BHH} have been presented to support the findings and arguments.

\subsection{Standalone vs. \ac{BHH} Baseline}
\label{sec:conclusion:results:summary:standalone}

For this experimental group the baseline \ac{BHH} was found to perform relatively well in comparison to the standalone low-level \index{heuristic}heuristics. Overall the \ac{BHH} ranked 5th out of 11 with performances close to that of the best \index{heuristic}heuristics. Unfortunately, the \ac{BHH} was not entirely able to beat the best heuristics on all occasions, but did perform comparatively well in all cases. The empirical results, statistical tests, descriptive plots and plots of example runs are given to support findings and conclusions.

\subsection{\ac{BHH} Variant: Heuristic pool}
\label{sec:conclusion:results:summary:heuristic_pool}

For this experimental group, different configurations of \index{heuristic}heuristic pools were considered. Three different configurations were evaluated. It was found that the gradient-only \ac{BHH} variant performed significantly better than the configurations that included all of the heuristics and one that included only the meta-heuristics. It was shown that the inclusion of meta-heuristics cause the \ac{BHH} to overfit much more drastically due to the nature of their update step operations.

\subsection{\ac{BHH} Variant: Population Size}
\label{sec:conclusion:results:summary:population_size}

For this experimental group, various different population sizes are evaluated. It was found that the population size is largely problem-dependent. An interesting observation was made where some cases where shown where the relationship between population size and performance is not linear, but rather parabolic or even polynomial in some cases. This warrants for further investigation and could serve as a good opportunity for future research.

\subsection{\ac{BHH} Variant: Credit}
\label{sec:conclusion:results:summary:credit}

For this experimental group, various different credit assignment strategies were evaluated. It was found that the choice of credit assignment strategy to use is largely problem-dependent. Two cases were highlighted where symmetric credit assignment was preferred, which suggests that for that dataset \index{heuristic}heuristic selection doesn't matter, only the proxied update step operations are sufficient.

\subsection{\ac{BHH} Variant: Reselection}
\label{sec:conclusion:results:summary:reselection}

For this experimental group different reselection window sizes were evaluated. It was found that a larger reselection size is generally preferred. A bigger reselection window sizes lead to a longer timeframe to learn before reselection has to occur. The increase in number of samples of evidence, per entity-heuristic combination in the performance log is argued to be the reason for this. However, that means that the reselection and replay window size parameter are related. If the reselection window size is large, the replay window size should be large as well.

\subsection{\ac{BHH} Variant: Replay}
\label{sec:conclusion:results:summary:replay}

For this experimental group, different replay windows sizes were evaluated. It was found that the replay window is problem-dependent with some dataset preferring short memory and other preferring long memory. Take note of the relationship between the reselection, replay and reanalysis window sizes. The value of the one does influence the value of other and should be carefully selection together.

\subsection{\ac{BHH} Variant: Reanalysis}
\label{sec:conclusion:results:summary:reanalysis}

For this experimental group different reanalysis window sizes were evaluated. It was also found that the reanalysis window size is problem-dependent. Given the relationship between the reselection, replay and reanalysis window sizes, a suggestion to eliminate hyper-parameters is to remove the notion of reanalysis and merge with reselection. Reselection is shown to correlate with reanalysis and thus can be removed by just setting the reanalysis window size equal to the reselection size.

\subsection{\ac{BHH} Variant: Burn In}
\label{sec:conclusion:results:summary:burn_in}

For this experimental group different burn in window sizes were evaluated. It was found that in general no burn in is preferred, but some exceptions preferring just a very small burn in. In general is was shown that large burn in values are not good.

\subsection{\ac{BHH} Variant: Normalise}
\label{sec:conclusion:results:summary:normalise}

For this experimental group an empirical test was conducted to determine the effects of normalisation of pseudo counts in the performance log. The choice of this parameter was shown to be problem depedent.

\subsection{\ac{BHH} Variant: Discounted Rewards}
\label{sec:conclusion:results:summary:discounted_rewards}

It can be concluded that the outcomes of the empirical process were successful and that the scientific process has been followed accordingly. From this, it can be concluded that all of the objective of the dissertation have been met and that the research can be concluded. The next section provides a brief discussion of further research opportunities that stem from this work.

\section{Further Research}
\label{sec:conclusion:further_research}

Throughout this dissertation, many different opportunities have been identified for future research. This section contains a summmary of these topics.

\subsubsection{Prior Knowledge}

The \ac{BHH} initialises the concentrations for its distributions symmetrically (a value of 1 for all indices). Symmetric initialisation contains no prior bias and assumes uniform sampling at first. It has been identified that expert knowledge can be incorporated into the \ac{BHH} by carefully providing the initial concentration for the distributions. This research would then evaluate if such prior information has a positive impact on the outcomes of the \ac{BHH}.

\subsubsection{Early Stopping}

It has been shown that the \ac{BHH} suffers drastically from overfitting as the majority of learning happens during the first few epochs (large datasets have more mini-batch iterations per epoch) resulting in the majority of the training process, which span 30 epochs, to try recover from overfitting. Early stop was purposefully not utilised in this research in order to see how the \ac{BHH} would behave after training has saturated. Early stopping could provide valuable insight into the actual ranked performance of the \ac{BHH} since overfitting would then no longer be present and a ranked performance evaluation can be done at some point in time.

\subsubsection{Entity Search}

For this dissertation, even though the predictive model implemented by the \ac{BHH} includes entity consideration, it does not sample from an entity pool, but rather keeps the entire entity pool and just switch allocated heuristics. The \ac{BHH}, as is, can be used to learn which entities to select as well. The hypothesis is that this would result in better combinations of entities and heuristics, more often, which should have a positive effect on the outcomes of the \ac{BHH}

\subsubsection{Models}

For this dissertation, focus was put on training \acp{FFNN}. However, in theory one should be able to swap out \acp{FFNN} for any other mathematical model that can be optimised. Suggestions include \acp{DNN}, \acp{RNN} and dynamic optimisation problems.

\subsubsection{Credit Search}

Credit assignment in the context of this dissertation was has 2 outcomes, true and false. Therefore, credit assignment and by definition performance evaluation is modeled as a \index{binomial distribution} distribution with a \index{Beta probability distribution}Beta probability distribution as a prior probability distribution. Heuristic selection has multiple possible outcomes, yielding a index associated with a heuristic. Therefore, heuristic selection is modeled as a \index{multionomial}multinomial/\index{categorical}categorical with a dirichlet probability distribution as a prior probability distribution. Since the dirichlet-multinomial distributions are the multivariate extensions of the beta-binomial distributions, it show be possible to extend credit assignment to a multivariate version. A suggestion then is to learn which credit assignment to select. The results of this have show that credit assignment is problem-dependent. Therefore, include credit selection as part of the selection pool implemented by the \ac{BHH}. One could then include multiple strategies, each with varying exploration-exploitation trade-off.

\subsubsection{Selection Validation}

The intent behind a selection validation mechanism is to confirm that selections are successful before they are utilised. In other words, a small verification window where it is decided whether the outcomes of a selection mechanism was beneficial to the learning outcomes or not. These selection validations are based on an ``acceptance criterion'' that a selection has to pass before it is validated. Inclusion of a selection validation mechanism for the \ac{BHH} could yield interesting outcomes.

>>>>

\begin{quotation}
      \noindent ``I am sorry to have made such a long speech, but I did not have time to make a shorter one.''
\end{quotation}
\begin{flushright}
      - Winston Churchill
\end{flushright}

This chapter provides a summary of the research that is done in this dissertation. The research objectives were set out in Chapter \ref{chap:introduction} and are concluded in this chapter. Furthermore, this chapter provides a summary of the results and findings from the empirical process and provides future research opportunities. The remainder of the chapter is structured as follows.

\begin{itemize}
      \item \textbf{Section \ref{sec:conclusion:research_goals}} provides a summary of the research intent and provides a review of the problem statement, objectives and motivations behind the research.

@@

      \item \textbf{Section \ref{sec:conclusion:bhh}} provides a brief summary of the \ac{BHH} and its implementation.

      \item \textbf{Section \ref{sec:conclusion:methodology}} provides a brief summary of the methodology and the empirical process that was followed.

      \item \textbf{Section \ref{sec:conclusion:results}} summarises the research findings. This section is broken down into the various experimental groups that were executed.

      \item \textbf{Section \ref{sec:conclusion:further_research}} presents future research opportunities.

      \item \textbf{Section \ref{sec:conclusion:documentation_and_data}} provides a brief discussion on supporting material related to the research, as made available by the authors.

      \item \textbf{Section \ref{sec:conclusion:summary}} provides a brief summary of the chapter.
\end{itemize}

\section{Summary of Research Intent}
\label{sec:conclusion:research_goals}

@@

\subsection{Review of Problem Statement}
\label{sec:conclusion:research_goals:problem_statement}

The main area of focus for the research done in this dissertation stems from the problem statement, which identified the difficult and tedious problem of selecting the best \index{heuristic}heuristic for training \acp{FFNN}. This process is often non-trivial and time-consuming. There is no easy way to know which \index{heuristic}heuristic to select to train \acp{FFNN}. Traditionally, an iterative approach of trial-and-error was followed. This process involves a tedious process of carefully considering and selecting candidate \index{heuristic}heuristics, whereby each candidate \index{heuristic}heuristic is then empirically tested and evaluated. This process is often executed at the expense of the researcher's resources.

\subsection{Review of Research Motivation}
\label{sec:conclusion:research_goals:motivations}

The research presented in this disseration identified the possibility of using a different approach, referred to as \acp{HH}, to automate the \index{heuristic}heuristic selection process. \acp{HH} are high-level search algorithms that search in the \index{heuristic}heuristic space, whereby low-level \index{heuristic}heuristics search in the solution space. \acp{HH} have been shown to provide a general solution to the \index{heuristic}heuristic selection process. The benefit that such an approach provides, is that it automates the \index{heuristic}heuristic selection process. This approach saves researchers time and potentially produce a solution that could generalise to multiple problems.

Investigation was done into the landscapes of existing solutions to train \acp{FFNN} as well as \acp{HH}. Though there exists many applications where \acp{HH} are used for optimisation, there are little to no published work on using \acp{HH} to train \acp{FFNN}. The only work that was found include the work by~\citeauthor{ref:nel:2021}~\cite{ref:nel:2021}.

\subsection{Review of Research Objectives}
\label{sec:conclusion:research_goals:research_objectives}

Existing techniques from other problem domains were considered. \acs{RL}, meta-learning and probabilistic learning approached were considered. Bayesian probability theory showed promise. This research then set out to develop a novel high-level \index{heuristic}heuristic that utilises probability theory in an online learning setting to drive the automatic \index{heuristic}heuristic selection process. As such, the \acs{BHH} was conceptualised. The research objectives were defined and are summarised as follows.

\begin{itemize}
      \item Conduct literature studies on all related topics that are relevant to the development of the \acs{BHH}. These include \acs{ANN}, existing low-level \index{heuristic}heuristics, meta-learning, \acp{HH}, probability theory and Bayesian statistics.

      \item Develop a novel \acs{BHH} that can be used to automate the \index{heuristic}heuristic selection process. The \acs{BHH} follows an approach that includes a selective and perturbative element in an online learning setting. Bayesian statistics and \acs{MAP} is used as the optimisation technique. Furthermore, the \acs{BHH} implements a mapping for proxied \index{heuristic}heuristic state update operations, whereby \index{heuristic}heuristic state is maintained by outsourcing state opertations to relevant low-level \index{heuristic}heuristics.

@@

      \item Conduct an empirical study to study the behavioural characteristics of the \acs{BHH}.

      \item Conduct an empirical study to critically evaluate the performance of the \acs{BHH} compared to traditional, low-level, standalone \index{heuristic}heuristic when training \acp{FFNN} on a number of different datasets.

      \item Conduct an empirical study to evaluate variants of the \acs{BHH} to study the impact of various hyper-parameters on the outcomes of the \ac{BHH}.

      \item Provide and discuss the findings of the results produced by the empirical process. The results are analysed for statistical significance.
\end{itemize}

The research objectives set out in this dissertation are extensive. Each of these research objectives have been successfully executed. From the findings made in this dissertation, many different opportunities for future research are identified.

@@

Chapters \ref{chap:anns}-\ref{chap:probability} provided the reader with the relevant background information that is necessary to develop the novel \acs{BHH}. Chapter~\ref{chap:anns} provided background information on \acp{ANN}. All the components that make up the \acs{AN} were provided and is followed by discussions on \acp{FFNN}. Chapter~\ref{chap:heuristics} provided background information on various low-level heuristics that are designed to train \acp{FFNN}. A number of gradient-based \index{heuristic}heuristics and \index{meta-heuristic}meta-heuristics were presented in detail. Chapter~\ref{chap:hhs} provided background information and literature reviews on \acp{HH}. Meta-learning is discussed and a \acs{HH} classification scheme, developed by \citeauthor{ref:burke:2010}~\cite{ref:burke:2010}, was discussed in detail. Chapter~\ref{chap:probability} provided background information and mathematical derivations on probability theory and Bayesian statistics. Various probability distributions were provided along with their conjugate priors. \acs{MLE} and \acs{MAP} were presented in detail along with mathematical breakdowns.

From the aforementioned chapters, it can be concluded that the necessary background information was provided as set out in the research objectives of this dissertation.

\section{Summary of The Bayesian Hyper-Heuristic}
\label{sec:conclusion:bhh}

The main contribution from this dissertation is the development of a novel \acf{BHH}. Chapter \ref{chap:bhh} provided the details on the concept and implementation of the \ac{BHH}. Various design decisions and hyper-parameters that could affect the outcomes of the \ac{BHH} were presented.

It was shown that the \acs{BHH} is a population-based, meta-hyper-heuristic that utilises selection and perturbation of low-level \index{heuristic}heuristics in an online learning fashion. \index{heuristic}Heuristics are selected for each entity in a population of entities that each implement a candidate solution to the underlying \acs{FFNN}. The \acs{BHH} uses a Bayesian probabilistic model to drive the \index{heuristic}heuristic selection process. \acs{MAP} was derived for the probabilistic model and is used as the mechanism by which the \acs{BHH} is optimised, yielding the learning capability of the \acs{BHH}.

Furthermore, it is shown that \index{heuristic}heuristic selection alone is not sufficient and that a mechanism of transition between \index{heuristic}heuristics is needed as they are selected for each entity in the population. Entity and \index{heuristic}heuristic state and state-manipulation formed the cornerstone of this topic. Perturbation of \index{heuristic}heuristics and solutions is achieved through a technique that deconstructs \index{heuristic}heuristics into their initialisation and update steps. The update operations for each heuristic was derived as movement equations borrowed from the field of physics. This technique allows for the proxying of update step operations as they are required by different \index{heuristic}heuristics.

Detailed discussions were provided on a number of hyper-parameters that each contribute to the trade-off between \index{heuristic}heuristic and solution exploration and exploitation. These hyper-parameters include the \index{heuristic pool}\textit{heuristic pool} configuration, the \textit{population size}, the \textit{credit assignment strategy} used, the \textit{reselection interval}, the \textit{replay window size}, the \textit{reanalysis interval}, the \textit{burn in window size}, \textit{normalisation} of concentration parameters and \textit{discounted rewards} as assigned by the credit assignment strategy. A \acs{BHH} baseline configuration was identified with default values for each of the hyper-parameters.

It was mentioned that the \acs{BHH}, implemented in this dissertation, does not implement a move-acceptance strategy that rejects heuristic progressions if they do not improve on the current best solution. Throughout the presentation of empirical results, it is recommended that this technique be investigated and implemented in further research.

@@

The research objectives defined a number of empirical tests to be executed. Each one of the empirical tests is referred to as an experimental group. Various experimental groups have been identified and are listed below.

\begin{itemize}
      \item An experimental group that provides a case-study on the behaviour of the \ac{BHH} as it relates to training of a \acs{FFNN} on an example dataset (iris), in order to understand the workings of the \acs{BHH}, and to determine if the \acs{BHH} is able to successfully train \acp{FFNN}. Three different configurations of the \acs{BHH} configuration was implemented. This includes the default \acs{BHH} baseline configuration, the \acs{BHH} baseline configuration where the replay window size is set to 250, and the \acs{BHH} baseline configuration which utilises the \textit{symmetric} credit assignment strategy.

      \item An experimental group that provides a comparative analysis between the performance of the \acs{BHH} baseline configuration and low-level, standalone \index{heuristic}heuristics when training \acp{FFNN} on a number of datasets.

      \item An experimental group that provides a comparative analysis between variants of the \ac{BHH} that investigate the effects of various hyper-parameters on the outcomes of the \acs{BHH}. These variants include:

            \begin{itemize}
                  \item The \acs{BHH} baseline configuration with different \index{heuristic pool}heuristic pool configurations. Three different \index{heuristic pool}heuristic pool configurations were implemented. These configurations include a configuration with all the low-level \index{heuristic}heuristics included in the \index{heuristic pool}heuristic pool, a configuration with only gradient-based \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and a configuration with only \index{meta-heuristic}meta-heuristics in the \index{heuristic pool}heuristic pool.

                  \item The \acs{BHH} baseline configuration with different population sizes. Five different population sizes were implemented including 5, 10, 15, 20, and 25.

                  \item The \acs{BHH} baseline configuration with different credit assignment strategies. Five different credit assignment strategies were implemented including the \textit{ibest}, \textit{pbest}, \textit{rbest}, \textit{gbest}, and \textit{symmetric} credit assignment strategies.

                  \item The \acs{BHH} baseline configuration with different reselection intervals. Five different reselection intervals were implemented including 1, 5, 10, 15, and 20.

                  \item The \acs{BHH} baseline configuration with different reanalysis window sizes. Five different reanalysis intervals were implemented including 1, 5, 10, 15, and 20.

                  \item The \acs{BHH} baseline configuration with different replay window sizes. Five different replay window sizes were implemented including 1, 5, 10, 15, and 20.

                  \item The \acs{BHH} baseline configuration with different burn in window sizes. Five different burn in window sizes were implemented including 0, 5, 10, 15, and 20.

                  \item The \acs{BHH} baseline configuration where normalisation of pseudo counts for concentration parameters, as derived from credit allocations in the performance log, are enabled and disabled.

                  \item The \acs{BHH} baseline configuration where discounted rewards of pseudo counts for concentration parameters, as derived from credit allocations in the performance log, are enabled and disabled.
            \end{itemize}
\end{itemize}

Each experimental group was executed against a set of fourteen datasets, consisting of regression and classification problems, split between uni- and multimodal problems. Each experimental group was repeated over 30 runs for statistical certainty. The statistical analysis process was discussed and the ANOVA, post hoc Tukey, independent T-test and Kruskal-Wallis statistical tests formed part of the statistical tests that were conducted.

All experimental groups were run for a maximum of 30 epochs in order to allow for the studying of the \ac{BHH} even after training has converged and overfitting has occured. The maximum epoch strategy yielded a training process that is longer than what was empirically found to be necessary. This also meant that no early stopping strategy was used. Future research opportunities should incorporate an early stopping strategy of the training process.

@@

This section provides a summary of the results obtained from each of the experimental groups that were executed. This section is structured as follows.

\begin{itemize}
      \item \textbf{Section \ref{sec:conclusion:results:summary:case_study}} provides a summary of the results for the experimental group that executed a case study on the behaviour of the \acs{BHH} on an example dataset.

      \item \textbf{Section \ref{sec:conclusion:results:summary:standalone}} provides a summary of the results for the experimental group that compares the performance of the \acs{BHH} baseline configuration with low-level, standalone \index{heuristic}heuristics, across all datasets.

      \item \textbf{Section \ref{sec:conclusion:results:summary:heuristic_pool}} provides a summary of the results for the experimental group that investigates the effects of the \index{heuristic pool}\textit{heuristic pool} hyper-parameter on the \acs{BHH}, across all datasets.

      \item \textbf{Section \ref{sec:conclusion:results:summary:population_size}} provides a summary of the results for the experimental group that investigates the effects of the \textit{population size} hyper-parameter on the \acs{BHH}, across all datasets.

      \item \textbf{Section \ref{sec:conclusion:results:summary:credit}} provides a summary of the results for the experimental group that investigates the effects of the \textit{credit assignment strategy} hyper-parameter on the \acs{BHH}, across all datasets.

      \item \textbf{Section \ref{sec:conclusion:results:summary:reselection}} provides a summary of the results for the experimental group that investigates the effects of the \textit{reselection interval} hyper-parameter on the \acs{BHH}, across all datasets.

      \item \textbf{Section \ref{sec:conclusion:results:summary:replay}} provides a summary of the results for the experimental group that investigates the effects of the \textit{replay window size} hyper-parameter on the \acs{BHH}, across all datasets.

      \item \textbf{Section \ref{sec:conclusion:results:summary:reanalysis}} provides a summary of the results for the experimental group that investigates the effects of the \textit{reanalysis interval} hyper-parameter on the \acs{BHH}, across all datasets.

      \item \textbf{Section \ref{sec:conclusion:results:summary:burn_in}} provides a summary of the results for the experimental group that investigates the effects of the \textit{burn in window size} hyper-parameter on the \acs{BHH}, across all datasets.

      \item \textbf{Section \ref{sec:conclusion:results:summary:normalise}} provides a summary of the results for the experimental group that investigates the effects of the \textit{normalisation} hyper-parameter on the \acs{BHH}, across all datasets.

      \item \textbf{Section \ref{sec:conclusion:results:summary:discounted_rewards}} provides a summary of the results for the experimental group that investigates the effects of the \textit{discounted rewards} hyper-parameter on the \acs{BHH}, across all datasets.
\end{itemize}

\subsection{Behavioural Case Study}
\label{sec:conclusion:results:summary:case_study}

For this experimental group it was found that the \ac{BHH} is able to train a \acf{FFNN} relatively well. Detailed analysis was provided for various state parameters maintained by the \acs{BHH}. These include the concentration parameters for different heuristics, probabilities of \index{heuristic}heuristic selection probabilities, prior heuristic selection probabilities and posterior heuristic selection probabilities. It was shown that the \ac{BHH} is able to learn and that the \acs{BHH} is able to exploit small performance biases as it relates to \index{heuristic}heuristic selection. This enables the \acs{BHH} to select the correct \index{heuristic}heuristics to apply to the correct entities at the correct time in the training process.

Various illustrations of the train and test loss plots, as it relates to training of a \acs{FFNN} on the the iris dataset, have been provided. Furthermore, various illustrations on the changes of the \acs{BHH} state parameters were provided for visual aid.

The main findings that were made for this experimental group are given as follows. Most of the training progression is made in the early stages of the training process. That leads to the conclusion that the \acs{BHH} has a small window from which it should learn and gain the most in the training process. After training has converged, the \acs{BHH} resets its concentration parameters and heuristic selection returns to the symmetric heuristic selection case. As such, the \acs{BHH} explores other heuristics in an attempt to further improve on the current best solution found. The test set was used as a validation set during training. Some overfitting can be observed as the \acs{BHH} tried finding better solutions on the train set, but at the cost of generalisation on the test set. Minor divergence of the training loss is observed as the \acs{BHH} explores other heuristics in an attempt to improve performance. Since no move-acceptance strategy, and no early stopping stategy was used, the \acs{BHH} could select heuristics that are sub-optimal. Future research opportunities should incorporate these aforementioned strategies.

\subsection{\acs{BHH} Baseline vs. Low-Level Heuristics}
\label{sec:conclusion:results:summary:standalone}

For this experimental group, three different configurations of the \acs{BHH} baseline configuration were implemented. These configurations vary in the type of \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool. The \textit{bhh\_all} configuration included all low-level \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool. The \textit{bhh\_gd} configuration included only gradient-based \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and the \textit{bhh\_mh} configuration included only \index{meta-heuristic}meta-heuristics in the \index{heuristic pool}heuristic pool.

Overall the \textit{bhh\_gd} configuration performed the best out of the \acs{BHH} variants, achieving an overall rank of fourth amongst thirteen \index{heuristic}heuristics that were implemented and executed on fourteen datasets. The \textit{bhh\_gd} configuration produced performance results close to that of the best low-level \index{heuristic}heuristics and was only statistically outperformed by the top two low-level \index{heuristic}heuristics. The \textit{bhh\_all} configuration achieved an overall rank of sixth and the \textit{bhh\_mh} achieved an overall rank of eighth.

Although the \textit{bhh\_gd} configuration produced performance results comparable to the best low-level heuristics, the \textit{bhh\_all} and \textit{bhh\_mh} configurations produced average results. It was found that, in general, gradient-based heuristics produced the best results, as such, it it understandable that the \textit{bhh\_gd}  yielded the best performance outcomes between the different \acs{BHH} variants that were implemented. Although the \acs{BHH} variants were not able to produce better results than the top low-level \index{heuristic}heuristics, the \acs{BHH} variants still effectively trained the underlying \acp{FFNN} and produced good training outcomes overall.

It was shown that the \textit{bhh\_gd} configuration produced the lowest variance in rank between datasets out of all of the \index{heuristic}heuristics implemented, giving the \acs{BHH} the ability to generalise well to other problems.

Furthermore, it was shown that the \acs{BHH} provides a mechanism whereby prior expert knowledge can be injected, before training starts. Future research can exploit this knowledge and provide a significant bias towards \index{heuristic}heuristics that are known to perform well on particular problem types.

\subsection{Heuristic pool}
\label{sec:conclusion:results:summary:heuristic_pool}

For this experimental group, the same three \index{heuristic pool}heuristical pool variants, as outlined for the \acs{BHH} behavioural case study, was implemented. These variants are denoted as \textit{all}, \textit{gd}, and \textit{mh}. This experimental group then provided an opportunity to look at the effects of the \index{heuristic pool}heuristic pool hyper-parameter in more detail.

As with the experimental group that compares the performance of the \acs{BHH} baseline configuration with low-level, standalone \index{heuristic}heuristics, it was found that the \textit{gd} configuration performed significantly better than the \textit{all} and \textit{mh} configurations overall, across all datasets.

The benefits of using meta-heuristics in the heuristic pool was not realised in this dissertation, since the gradient-based low-level \index{heuristic}heuristics, as well as the \textit{gd} configuration produced the best overall performance, across all datasets.

\subsection{Population Size}
\label{sec:conclusion:results:summary:population_size}

For this experimental group, five different population sizes were evaluated. These included population sizes of 5, 10, 15, 20, and 25. It was found that lower population sizes yielded better results on the majority of datasets, while only some datasets prefer larger population sizes. However, overall it was shown that the population size hyper-parameter is problem specific. Illustrations of the train and test, loss and accuracy plots for some example datasets were provided. Some divergence in training loss was observed and was attributed to selection of \index{heuristic}heuristics that yield sub-optimal results after an optimal solution has already been found. As before, a move acceptance strategy and an early stopping strategy can be incorporated to avoid this effect.

\subsection{Credit Assignment Strategy}
\label{sec:conclusion:results:summary:credit}
